### 2022-02-06 README.Rmd
Deploying to gh-pages from @ gavinsimpson/gratia@4adf7ccf520acdb6071d6e4d546d11a6c7050e2f 🚀

* A *ggplot2*-based replacement for `mgcv:::plot.gam()`: `draw(gam_model)`.

@@

* Estimatation of derivatives of fitted smoothers: `derivatives()` (older functionality in `fderiv(gam_model)`),

* Estimation of point-wise across-the-function confidence intervals and simultaneous intervals for smooths: `confint(gam_model)`.

@@

*gratia* grew out of an earlier package, *schoenberg*, itself a development of the earlier package *tsgam*, which was originally intended to be used with GAMs fitted to time series. As I was developing *tsgam* however it became clear that the package could be used more generally and that the name "tsgam" was no longer appropriate. To avoid breaking blog posts I had written using *tsgam* I decided to copy the git repo and all the history to a new repo for the package under the name *schoenberg*. At a later date someone released another package called *schoenberg* to CRAN, so that scuppered that idea. Now I'm calling the package *gratia*. Hopefully I won't have to change it again…

>>>>

* A *ggplot2*-based replacement for `mgcv:::plot.gam()`: `draw.gam()`.

@@

* Estimatation of derivatives of fitted smoothers: `derivatives()`,

* Estimation of point-wise across-the-function confidence intervals and
  simultaneous intervals for smooths: `confint.gam()`.

@@

*gratia* grew out of an earlier package, *schoenberg*, itself a development of
the earlier package *tsgam*, which was originally intended to be used with GAMs
fitted to time series. As I was developing *tsgam* however it became clear that
the package could be used more generally and that the name "tsgam" was no longer
appropriate. To avoid breaking blog posts I had written using *tsgam* I decided
to copy the git repo and all the history to a new repo for the package under the
name *schoenberg*. At a later date someone released another package called
*schoenberg* to CRAN, so that scuppered that idea. Now I'm calling the package
*gratia*. Hopefully I won't have to change it again&hellip;
